\bf The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-08-10 paper/paper.Rmd
eval = FALSE

```{r internal, echo = FALSE}
# Internal: after removing trees in buffer and have NA for growth, there is one
# tree that is not included in focal_vs_comp_scbi b/c it has no neighbors within
# comp_dist = 7.5m of it
growth_scbi %>%
  filter(!buffer & !is.na(growth)) %>%
  filter(!stemID %in% focal_vs_comp_scbi$focal_ID)

>>>>

```{r internal, echo = FALSE, eval = FALSE}
# Internal: after removing trees in buffer and have NA for growth, there is one
# tree that is not included in focal_vs_comp_scbi b/c it has no neighbors within
# comp_dist = 7.5m of it
growth_scbi %>%
  filter(!buffer & !is.na(growth)) %>%
  filter(!stemID %in% focal_vs_comp_scbi$focal_ID)

### 2021-08-10 paper/paper.tex
No longer eval appendix 1
eval = FALSE

\begin{verbatim}
## Simple feature collection with 1 feature and 17 fields
## Geometry type: POINT
## Dimension:     XY
## Bounding box:  xmin: 250 ymin: 582 xmax: 250 ymax: 582
## CRS:           NA
## # A tibble: 1 x 18
##   stemID sp     dbh1 codes1 status  dbh2 codes2 growth
## *  <dbl> <fct> <dbl> <chr>  <chr>  <dbl> <chr>   <dbl>
## 1  18823 quve   68.8 NULL   A       69.9 NULL    0.215
## # ... with 10 more variables: geometry <POINT>, family <chr>,
## #   genus <chr>, species <chr>, canopy_position <chr>,
## #   drought_tolerance <chr>, basal_area <dbl>, agb <dbl>, buffer <lgl>,
## #   foldID <fct>
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{Figures/internal-1} \end{center}

@@

    \CommentTok{# Status update}
    \KeywordTok{str_c}\NormalTok{(}\StringTok{"Shuffle with permutation "}\NormalTok{, j, }\StringTok{" at "}\NormalTok{, }\KeywordTok{Sys.time}\NormalTok{()) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{print}\NormalTok{()}
\NormalTok{\}}
\CommentTok{## [1] "Shuffle with permutation 1 at 2021-08-09 18:21:51"}
\CommentTok{## [1] "Shuffle with permutation 2 at 2021-08-09 18:26:48"}
\CommentTok{## [1] "Shuffle with permutation 3 at 2021-08-09 18:31:46"}
\CommentTok{## [1] "Shuffle with permutation 4 at 2021-08-09 18:36:41"}
\CommentTok{## [1] "Shuffle with permutation 5 at 2021-08-09 18:41:31"}
\CommentTok{## [1] "Shuffle with permutation 6 at 2021-08-09 18:46:03"}
\CommentTok{## [1] "Shuffle with permutation 7 at 2021-08-09 18:50:32"}
\CommentTok{## [1] "Shuffle with permutation 8 at 2021-08-09 18:55:09"}
\CommentTok{## [1] "Shuffle with permutation 9 at 2021-08-09 18:59:38"}
\CommentTok{## [1] "Shuffle with permutation 10 at 2021-08-09 19:04:06"}
\CommentTok{## [1] "Shuffle with permutation 11 at 2021-08-09 19:08:36"}
\CommentTok{## [1] "Shuffle with permutation 12 at 2021-08-09 19:13:01"}
\CommentTok{## [1] "Shuffle with permutation 13 at 2021-08-09 19:17:25"}
\CommentTok{## [1] "Shuffle with permutation 14 at 2021-08-09 19:21:47"}
\CommentTok{## [1] "Shuffle with permutation 15 at 2021-08-09 19:26:20"}
\CommentTok{## [1] "Shuffle with permutation 16 at 2021-08-09 19:30:42"}
\CommentTok{## [1] "Shuffle with permutation 17 at 2021-08-09 19:35:05"}
\CommentTok{## [1] "Shuffle with permutation 18 at 2021-08-09 19:39:28"}
\CommentTok{## [1] "Shuffle with permutation 19 at 2021-08-09 19:43:51"}
\CommentTok{## [1] "Shuffle with permutation 20 at 2021-08-09 19:48:14"}
\CommentTok{## [1] "Shuffle with permutation 21 at 2021-08-09 19:52:37"}
\CommentTok{## [1] "Shuffle with permutation 22 at 2021-08-09 19:57:01"}
\CommentTok{## [1] "Shuffle with permutation 23 at 2021-08-09 20:01:29"}
\CommentTok{## [1] "Shuffle with permutation 24 at 2021-08-09 20:06:09"}
\CommentTok{## [1] "Shuffle with permutation 25 at 2021-08-09 20:10:42"}
\CommentTok{## [1] "Shuffle with permutation 26 at 2021-08-09 20:15:06"}
\CommentTok{## [1] "Shuffle with permutation 27 at 2021-08-09 20:19:29"}
\CommentTok{## [1] "Shuffle with permutation 28 at 2021-08-09 20:23:52"}
\CommentTok{## [1] "Shuffle with permutation 29 at 2021-08-09 20:28:15"}
\CommentTok{## [1] "Shuffle with permutation 30 at 2021-08-09 20:32:37"}
\CommentTok{## [1] "Shuffle with permutation 31 at 2021-08-09 20:36:59"}
\CommentTok{## [1] "Shuffle with permutation 32 at 2021-08-09 20:41:21"}
\CommentTok{## [1] "Shuffle with permutation 33 at 2021-08-09 20:45:43"}
\CommentTok{## [1] "Shuffle with permutation 34 at 2021-08-09 20:50:06"}
\CommentTok{## [1] "Shuffle with permutation 35 at 2021-08-09 20:54:29"}
\CommentTok{## [1] "Shuffle with permutation 36 at 2021-08-09 20:58:51"}
\CommentTok{## [1] "Shuffle with permutation 37 at 2021-08-09 21:03:16"}
\CommentTok{## [1] "Shuffle with permutation 38 at 2021-08-09 21:07:38"}
\CommentTok{## [1] "Shuffle with permutation 39 at 2021-08-09 21:12:01"}
\CommentTok{## [1] "Shuffle with permutation 40 at 2021-08-09 21:16:24"}
\CommentTok{## [1] "Shuffle with permutation 41 at 2021-08-09 21:20:47"}
\CommentTok{## [1] "Shuffle with permutation 42 at 2021-08-09 21:25:11"}
\CommentTok{## [1] "Shuffle with permutation 43 at 2021-08-09 21:29:34"}
\CommentTok{## [1] "Shuffle with permutation 44 at 2021-08-09 21:33:57"}
\CommentTok{## [1] "Shuffle with permutation 45 at 2021-08-09 21:38:20"}
\CommentTok{## [1] "Shuffle with permutation 46 at 2021-08-09 21:42:42"}
\CommentTok{## [1] "Shuffle with permutation 47 at 2021-08-09 21:47:05"}
\CommentTok{## [1] "Shuffle with permutation 48 at 2021-08-09 21:51:27"}
\CommentTok{## [1] "Shuffle with permutation 49 at 2021-08-09 21:56:05"}

@@

\begin{center}\includegraphics[width=1\linewidth]{Figures/appendix1-code-1} \end{center}

>>>>

@@

    \CommentTok{# Status update}
    \KeywordTok{str_c}\NormalTok{(}\StringTok{"Shuffle with permutation "}\NormalTok{, j, }\StringTok{" at "}\NormalTok{, }\KeywordTok{Sys.time}\NormalTok{()) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{print}\NormalTok{()}
\NormalTok{\}}

@@
